Tuning parameter selection for a penalized estimator of species richness

### 2019-06-14 rre_manuscript/paper.tex
edit label

\label{sec:literature_review}

The classical model for estimating species abundance is a Poisson mixture model.  Under this model the number of times we observe an species $i$ is $X_i \sim \text{Poisson}(\Lambda)$ where $\Lambda$ is a random variable distributed according to some mixing distribution.
Many mixing distributions have been proposed (see, e.g., \cite{bulmer_1974,ord_1986,norris_1998}, and \cite{bunge_1993} for a comprehensive review). While our proposal may be easily generalized to other mixing distributions, in this paper we consider the simple, interpretable gamma distribution, which was first proposed to model species abundances by \citet{fisher_1943}.
Let $f_k = \#\{i: X_i = k\}$ be the number of classes observed $k$ times, called the \textit{frequencies} or \textit{frequency counts}.  Then the set $\{f_k\}_{k \geq 1}$ is a \textit{frequency count table}, a common way to represent species abundance data. The species problem is to predicte $f_0$, because $C = f_0 + f_1 + f_2 + \dots = f_0 + c$.

>>>>

\label{sec:literature_review}
\amy{up to here with editing}
The classical model for estimating species abundance is a Poisson mixture model.  Under this model the number of times we observe an species $i$ is $X_i \sim \text{Poisson}(\Lambda)$ where $\Lambda$ is a random variable distributed according to some mixing distribution.
Many mixing distributions have been proposed (see, e.g., \cite{bulmer_1974,ord_1986,norris_1998}, and \cite{bunge_1993} for a comprehensive review). While our proposal may be easily generalized to other mixing distributions, in this paper we consider the simple, interpretable gamma distribution, which was first proposed to model species abundances by \citet{fisher_1943}.
Let $f_k = \#\{i: X_i = k\}$ be the number of classes observed $k$ times, called the \textit{frequencies} or \textit{frequency counts}.  Then the set $\{f_k\}_{k \geq 1}$ is a \textit{frequency count table}, a common way to represent species abundance data. The species problem is predicting $f_0$, because $C = f_0 + f_1 + f_2 + \dots = f_0 + c$.
